### 2017-02-22 Theory/Theory.tex
Some more editing

m_{A}^2\sin{\beta}^2 + m_{Z}^2\cos{\beta}^2 & -(m_{A}^2+m_{Z}^2)\sin{\beta}\cos{\beta}\\
-(m_{A}^2+m_{Z}^2)\sin{\beta}\cos{\beta} & m_{A}^2\cos{\beta}^2+m_{Z}^2\sin{\beta}^2 \end{pmatrix},

@@

m_{\PHiggs,\PHiggslight}^2 = \frac{1}{2}[m_{A}^2+m_{Z}^2 \pm \sqrt{(m_A^2+m_Z^2)^2-4m_Z^2m_A^2\cos{2\beta}^2}].

@@

m_{h} \leq m_{Z},

@@

\cos{(\beta-\alpha)}^2 = \frac{m_h^2(m_Z^2-m_h^2)}{m_A^2(m_H^2-m_h^2)}.

@@

The requirement that $m_h$ be less than the mass of the Z boson, $91.2\,\GeV$, seems 
problematic at first, as it is known that there is a Higgs state with a mass of $125\,\GeV$. However,
the tree-level masses and couplings of the Higgs bosons in the MSSM can be
significantly altered by radiative corrections. The dominant effect is from
incomplete cancellation of the stop- and top-loop corrections. This can increase the mass
of the light Higgs boson up to a maximum of $135\,\GeV$.

@@

In the \textit{decoupling limit}, when \mA$>>m_{Z}$ and $\cos{(\beta-\alpha)}$ tends
to 0, the mixing
angle $\alpha \approx \beta - \pi/2$. This reduces the couplings in table
\ref{tab:mssm_couplings} to the \ac{SM} couplings for the \PHiggslight boson, 
with negligible couplings to bosons for the two remaining neutral
Higgs bosons, couplings to down-type quarks and leptons enhanced by a factor \tanb,
and couplings to up-type quarks enhanced by a factor $\frac{1}{\tan{\beta}}$. This motivates
the choice of decay into $\Pgt\Pgt$ as a search channel for the neutral Higgs bosons in the \ac{MSSM}.
Figure \ref{fig:mssm_brtautau} shows the branching ratios of the \PHiggs boson 
in the $m_{h}^{\text{mod+}}$ scenario
which will be discussed in more detail in section \ref{sec:theory_BSM_models_mhmodp}. 
The branching ratio into di-$\Pgt$ pairs is large for \tanb=30. The branching ratios 
 of the \PHiggsps boson follow a similar pattern.
%Using trigon identities: cos alpha/cos beta = cos (beta-pi/2)/cos beta = cosbeta*cospi/2 + sin(beta)*sin(pi/2) over cos beta = sin beta /cos beta = tan beta
%sin alpha = sin (beta-pi/2) = sinbeta cos pi/2 - cosbetasinpi/2 = -cosbeta 
%such that -sinalpha/cosbeta = 1
%cos alpha/sin beta = sin beta/sin beta = 1
%sin beta-alpha = sin pi/2 = 1
%cos beta-alpha = cos pi/2 = 0
%sin alpha/sin beta = -cos beta/sin beta=-1/tan(beta)

\begin{figure}[h!]
\begin{center}
\subfloat[\tanb=5]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/YR4HXS_BRSummary_H_mhmodp_tanbeta5_FeynHiggs_HDecay.pdf}}
\subfloat[\tanb=30]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/YR4HXS_BRSummary_H_mhmodp_tanbeta30_FeynHiggs_HDecay.pdf}}
\end{center}
\caption{Branching ratios of the \PHiggs boson in the $m_{h}^{\text{mod+}}$ scenario,
at (a) \tanb=5~and (b) \tanb=30. The branching ratio into $\tau\tau$ (blue), $b\bar{b}$ (red) 
and $\mu\mu$ (yellow) is enhanced at high \tanb, while the branching ratio into 
WW (grey) and \ttbar (green) is reduced \cite{MSSM-xswg-twiki}.}
\label{fig:mssm_brtautau}
\end{figure}

The dominant neutral MSSM Higgs boson production processes at hadron colliders
are slightly different from the \ac{SM} Higgs boson production processes. 
Because the pseudoscalar A does not couple to the
vector bosons, and in the decoupling limit the coupling of \PHiggs to vector
bosons is suppressed with respect to the \ac{SM} expectation, VBF and \PW/\PZ associated
production are not as important as for the production of the \ac{SM} Higgs boson. As in the \ac{SM}, gluon fusion production is 
the dominant production mode at low \tanb.
An example tree-level Feynman diagram for gluon fusion production, which proceeds via
a quark loop, is given in figure \ref{fig:production_mssm}a.
At low \tanb~values this loop is dominated by top quarks, while at 
high \tanb~the b-quark loop dominates. This is a result of the enhanced coupling to down-type fermions at high \tanb. 
Due to the negative top-bottom loop interference effect the gluon fusion cross section decreases with increasing \tanb~up
to around \tanb=3, when the cross section starts to increase with increasing \tanb~again.

@@

There are several different types of \ac{2HDM}, all distinguished by the couplings
of the different Higgs states to bosons and fermions. In its most general
form, there are 9 free parameters in the potential of a CP-conserving 2HDM. 
These are taken as \tanb, the mixing angle $\alpha$, already discussed in 
the context of the \ac{MSSM}, the masses of the five Higgs bosons,
and quartic couplings appearing in the potential. The most studied of the
\ac{2HDM}s, the type-II \ac{2HDM}, has a structure very similar to 
the MSSM Higgs sector. The tree-level couplings of the neutral Higgs bosons to 
vector bosons and fermions are the same as the tree-level \ac{MSSM} couplings 
in table \ref{tab:mssm_couplings}. %The decay \AtoZh is also possible,
%the \AtoZh~coupling is proportional to $\cos{(\beta-\alpha)}, like the \Htohh~coupling.

@@

\begin{figure}[h!]
\begin{center}
\subfloat[\PHiggs]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/typeII2HDMxsbr.png}}
\subfloat[\PHiggsps]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/typeII2HDMxsbrA.png}}
\end{center}
\caption[Inclusive production cross--section times branching ratio for an example of a type-II 2HDM, for the \PHiggs and \PHiggsps boson.]{Inclusive production cross--section times branching ratio for an example
of a type-II \ac{2HDM}, for (a) the \PHiggs boson and (b) the \PHiggsps boson. The
top figures use \tanb=1 and $\cos{(\beta-\alpha)}=-0.11$, the bottom
figures are made for \tanb=10 and $\cos{(\beta-\alpha)}=-0.02$. At low \tanb~the \Htohh and
\AtoZh decays are enhanced for masses up to $350\,\GeV$ \cite{2HDM-II}.}
\label{fig:2hdm_Hxsbr}
\end{figure}

@@

The parameters that need to be fixed in the benchmark scenarios are the 
\ac{SUSY} breaking scale $M_{\text{SUSY}}$, which is also the mass scale of the third generation squarks.
In addition, the higgsino mass parameter $\mu_{\text{MSSM}}$, and the U(1) and SU(2) gaugino mass parameters, $M_1$ and $M_2$, need to be fixed.
A choice for the masses of the stau ($m_{\tilde{\ell}_3}$) and the gluino ($m_{\tilde{g}}$) also needs to be made. The 
trilinear couplings of the stops, sbottoms and staus to the Higgs field ($A_t$, $A_b$ and $A_{\Pgt}$) and the 
stop, sbottom and stau mixing parameters ($X_t$, $X_b$ and $X_{\tau}$) are also fixed.

Some of these parameters can be related to each other. For example,
$X_t$, $X_b$ and $X_{\Pgt}$ can be expressed as:
\begin{equation}\label{eqn:trilinear_couplings}
\begin{split}
&X_t = A_t-\mu_{\text{MSSM}}\cot{\beta},\\
&X_b = A_b-\mu_{\text{MSSM}}\tan{\beta},\\
&X_{\Pgt} = A_{\Pgt} - \mu_{\text{MSSM}}\tan{\beta}.
\end{split}
\end{equation}
In addition, $M_1$ is fixed via the unification
relation,
\begin{equation}
M_1 = \frac{5}{3}M_2\tan{\theta_w}^2.
\end{equation}
%where $\theta_w$ is defined by $\cos{\theta_w} = \frac{m_W}{m_Z}$.
Some additional parameters which only have a
small effect on the MSSM Higgs boson sector are 
fixed to values compatible with 
exclusion limits from direct searches in all benchmark scenarios. The masses
of the first and second generation squarks are set to $1.5\,\TeV$, 
and the masses of the first and second generation sleptons to $500\,\GeV$. The trilinear
couplings of the first and second generation squarks and sleptons are taken to be 0.
%Since the discovery of the 125 GeV Higgs boson, only the MSSM benchmark
%scenarios 
%which contain a light Higgs boson with a mass of around 125 GeV
%are still accessible.
% in the mmax scenario the benchmark values have been chosen h
%such that the mass of the light CP-even Higgs boson is maximized for fixed tanβ and large
%MA (the scale of the soft SUSY-breaking masses in the stop and sbottom sectors, which
%sets the mass scale for the corresponding supersymmetric particles, has been fixed to 1 TeV
%in this scenario). This scenario is useful to obtain conservative bounds on tanβ for fixed
%values of the top-quark mass

\subsection{The $m_{h}^{\text{mod+}}$ scenario}
\label{sec:theory_BSM_models_mhmodp}
The $m_{\PHiggslight}^{\text{mod+}}$ scenario \cite{MSSM-benchmark-scenarios}
is a modification of the $m_{\PHiggslight}^{\text{max}}$ scenario \cite{MSSM-mhmax}. The $m_h^{\text{max}}$ scenario, which
was used for interpretations of \ac{MSSM}
 Higgs boson searches at LEP and the Tevatron, allows
the mass of the light Higgs boson to reach the highest a-priori expected 
value of around $135\,\GeV$ for high \mA. There is only a small area of the \mA-\tanb~plane
in this scenario where the mass of the light Higgs boson is compatible with the
observed $125\,\GeV$ state. The modifications to the parameters of the $m_{\PHiggslight}^{\text{max}}$ 
scenario address this issue. In the $m_{\PHiggslight}^{\text{mod+}}$ scenario $M_{\text{SUSY}}$ is chosen
to be $1\,\TeV$. The stop mixing parameter is positive, $X_t= 1.5 M_{\text{SUSY}}$.
%This gives better agreement with muon g-2 results while the mhmod- scenario
%negative stop mixing (-1.9 M_SUSY) results in better agreements with B(b->sgamma) 
%meausrements 
The remaining parameters are set as $\mu_{\text{MSSM}}=200\,\GeV$, $m_{\tilde{g}} = 1.5\,\TeV$,
$m_{\tilde{\ell}_3} = 1\,\TeV$, and $A_b=A_t=A_{\Pgt}$. 
%Figure \ref{fig:mhmodp_mh}a
%shows the mass of the light Higgs boson in the $m_{h}^{\text{mod+}}$ scenario, showing
%that its mass is compatible with 125 GeV over a large part of the parameter space. Masses within 
%a window $\pm 3$ GeV around 125 GeV are considered compatible with 125 GeV, where the 3 GeV
%variation corresponds to the theoretical uncertainty on the \ac{MSSM} prediction for \mh.

Figure \ref{fig:mhmodp_xs} shows the cross sections of
gluon fusion and b-associated production of the \PHiggs boson 
in the $m_h^{\text{mod+}}$ scenario. Gluon fusion 
production dominates at low \tanb, while b-associated production has a larger cross section
at high \tanb. The behaviour of the production cross sections of the \PHiggsps boson
is similar.

@@

Two approches for the definition of an \ac{MSSM} scenario that gives
access to the low-\tanb~region have been developed, they will be
discussed in the next sections.

\subsubsection{The low-\tanb-scenario}
\label{sec:theory_BSM_model_lowtb}
In the low-\tanb-scenario \cite{Hein-low-tb-high,MSSM-lowtanb}, the SUSY parameters entering
the radiative corrections are tuned to obtain light 
Higgs boson masses of around $125\,\GeV$ in most of the \mA-\tanb~plane considered.
Figure \ref{fig:mhmodp_mh}b shows that, apart from in a corner of \tanb~1-4 and 
\mA~$150$--$250\,\GeV$, \mh~is compatible with $125\,\GeV$.

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{\PHiggslight}^{\text{mod}+}$ scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_mhmodp.pdf}}
\subfloat[low \tanb~scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_lowtbhigh.pdf}}
\end{center}
\caption[The mass of the light Higgs boson, \mh, as a function of \mA~and
\tanb~in the $m_{\PHiggslight}^{\text{mod+}}$ scenario and the low \tanb~scenario.]{The mass of the light Higgs boson, \mh, as a function 
of \mA~and \tanb~in (a) the $m_{\PHiggslight}^{\text{mod+}}$ scenario and (b) the low \tanb~scenario. The white areas
indicate masses lower than $122\,\GeV$. The figures shows that
the mass of the light Higgs boson is compatible with $125\,\GeV$ over a large
part of the \mA-\tanb~plane in the $m_{\PHiggslight}^{\text{mod+}}$ scenario, except at low \tanb. In the low-\tanb~scenario
the mass of the light Higgs boson is compatible with $125\,\GeV$ nearly everywhere.}
\label{fig:mhmodp_mh}
\end{figure}
%\begin{figure}[h!]
%\begin{center}
%\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_lowtbhigh.png}
%\end{center}
%\caption{Mass of the light Higgs boson in the \mA-\tanb~plane of the low-\tanb~scenario.
%The mass is compatible with $125\,\GeV$ nearly everywhere \cite{MSSM-lowtanb}.}
%\label{fig:lowtbhigh_mh}
%\end{figure}
To obtain \mh$\approx125\,\GeV$ over a large part of the parameter
space, 
$M_{\text{SUSY}}$ is not fixed but varies between a few TeV and 100 TeV, while
varying the parameter $X_t$ as:
\begin{equation}
\begin{split}
\tan{\beta} \leq 2 &: \frac{X_t}{M_{\text{SUSY}}} = 2,\\
2 < \tan{\beta} \leq 8.6 &: \frac{X_t}{M_{\text{SUSY}}} = 0.0375\text{tan}^2\beta - 0.7\tan{\beta} + 3.25,\\
8.6 < \tan{\beta} &: \frac{X_t}{M_{\text{SUSY}}} = 0.
\end{split}
\end{equation}
The other trilinear couplings are set to 2 TeV, with $\mu_{\text{MSSM}}$ set to 1.5 TeV and $M_2$ to 2 TeV.

@@

One of the assumptions of the hMSSM is that 
the mass matrix for the neutral CP-even states can
be decomposed as,
\begin{equation}
\label{eqn:hmssm_massmatrix}
\mathcal{M}^2_{\phi} = \mathcal{M}^2_{\text{tree}} + \begin{pmatrix}
\Delta\mathcal{M}^2_{11} & \Delta\mathcal{M}^2_{12} \\
\Delta\mathcal{M}^2_{12} & \Delta\mathcal{M}^2_{22} \end{pmatrix},
\end{equation}
where the $\Delta\mathcal{M}^2_{ij}$ are the radiative corrections.
The second assumption is that only $\Delta\mathcal{M}^2_{22}$ needs to be
taken into account, as this is the element that involves the stop-top correction
and so $\Delta\mathcal{M}^2_{22} >> \Delta\mathcal{M}^2_{12},\Delta\mathcal{M}^2_{11}$. 
Finally, all SUSY particles are assumed to be heavy enough not to be
detected at the \acs{LHC} and apart from effects on the mass matrix, 
the effects on the Higgs sector can be neglected.
%all SUSY particles are heavy enough to escape detection at the LHC, and their effects on the Higgs sector other than those on the mass matrix, e.g. via direct loop corrections to the Higgs-boson couplings or via modifications of the total decay widths, can be neglected.

Using these assumptions the lightest eigenvalue
of the mass matrix can be inverted to get: 
\begin{equation}
\label{eqn:hmssm_deltam22}
\Delta\mathcal{M}^2_{22} = \frac{m_h^2(m_A^2+m_Z^2 - m_h^2) - m_A^2m_Z^2\text{cos}^22\beta}{m_Z^2\text{cos}^2\beta + m_A^2\text{sin}^2\beta - m_h^2},
\end{equation}

>>>>

m_{\PHiggsps}^2\sin{\beta}^2 + m_{\PZ}^2\cos{\beta}^2 & -(m_{\PHiggsps}^2+m_{\PZ}^2)\sin{\beta}\cos{\beta}\\
-(m_{\PHiggsps}^2+m_{\PZ}^2)\sin{\beta}\cos{\beta} & m_{\PHiggsps}^2\cos{\beta}^2+m_{\PZ}^2\sin{\beta}^2 \end{pmatrix},

@@

m_{\PHiggs,\PHiggslight}^2 = \frac{1}{2}[m_{\PHiggsps}^2+m_{\PZ}^2 \pm \sqrt{(m_{\PHiggsps}^2+m_{\PZ}^2)^2-4m_{\PZ}^2m_{\PHiggsps}^2\cos{2\beta}^2}].

@@

m_{\PHiggslight} \leq m_{\PZ},

@@

\cos{(\beta-\alpha)}^2 = \frac{m_{\PHiggslight}^2(m_{\PZ}^2-m_{\PHiggslight}^2)}{m_{\PHiggsps}^2(m_{\PHiggs}^2-m_{\PHiggslight}^2)}.

@@

The requirement that $m_{\PHiggslight}$ be less than the mass of the \PZ boson, $91.2\,\GeV$, seems 
problematic at first, as it is known that there is a Higgs state with a mass of $125\,\GeV$. However,
the tree-level masses and couplings of the Higgs bosons in the \ac{MSSM} can be
significantly altered by radiative corrections. The dominant effect is from
incomplete cancellation of the stop- and top-loop corrections. This can increase the mass
of the light Higgs boson up to a maximum of $135\,\GeV$.

@@

In the \textit{decoupling limit}, when $m_{\PHiggsps} \gg m_{\PZ}$ and $\cos{(\beta-\alpha)}$ tends
to 0, the mixing
angle $\alpha \approx \beta - \pi/2$. This reduces the couplings in table
\ref{tab:mssm_couplings} to the \ac{SM} couplings for the \PHiggslight boson, 
with negligible couplings to bosons for the two remaining neutral
Higgs bosons, couplings to down-type quarks and leptons enhanced by a factor \tanb,
and couplings to up-type quarks enhanced by a factor $\frac{1}{\tan{\beta}}$. This motivates
the choice of decay into $\Pgt\Pgt$ as a search channel for the neutral Higgs bosons in the \ac{MSSM}.
Figure \ref{fig:mssm_brtautau} shows the branching ratios of the \PHiggs boson 
in the $m_{\PHiggslight}^{\text{mod+}}$ scenario
which will be discussed in more detail in section \ref{sec:theory_BSM_models_mhmodp}. 
The branching ratio into di-tau pairs is large for \tanb~$= 30$. The branching ratios 
 of the \PHiggsps boson follow a similar pattern.
%Using trigon identities: cos alpha/cos beta = cos (beta-pi/2)/cos beta = cosbeta*cospi/2 + sin(beta)*sin(pi/2) over cos beta = sin beta /cos beta = tan beta
%sin alpha = sin (beta-pi/2) = sinbeta cos pi/2 - cosbetasinpi/2 = -cosbeta 
%such that -sinalpha/cosbeta = 1
%cos alpha/sin beta = sin beta/sin beta = 1
%sin beta-alpha = sin pi/2 = 1
%cos beta-alpha = cos pi/2 = 0
%sin alpha/sin beta = -cos beta/sin beta=-1/tan(beta)

\begin{figure}[h!]
\begin{center}
\subfloat[\tanb=5]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/YR4HXS_BRSummary_H_mhmodp_tanbeta5_FeynHiggs_HDecay.pdf}}
\subfloat[\tanb=30]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/YR4HXS_BRSummary_H_mhmodp_tanbeta30_FeynHiggs_HDecay.pdf}}
\end{center}
\caption[Branching ratios of the \PHiggs boson in the $m_{\PHiggslight}^{\text{mod+}}$ scenario]{Branching ratios of the \PHiggs boson in the $m_{\PHiggslight}^{\text{mod+}}$ scenario,
at (a) \tanb=5~and (b) \tanb=30. The branching ratio into $\tau\tau$ (blue), $b\bar{b}$ (red) 
and $\mu\mu$ (yellow) is enhanced at high \tanb, while the branching ratio into 
WW (grey) and \ttbar (green) is reduced \cite{MSSM-xswg-twiki}.}
\label{fig:mssm_brtautau}
\end{figure}

The dominant neutral MSSM Higgs boson production processes at hadron colliders
are slightly different from the \ac{SM} Higgs boson production processes. 
Because the pseudoscalar A does not couple to the
vector bosons, and in the decoupling limit the coupling of \PHiggs to vector
bosons is suppressed with respect to the \ac{SM} expectation, VBF and \PW or \PZ associated
production are not as important as for the production of the \ac{SM} Higgs boson. As in the \ac{SM}, gluon fusion production is 
the dominant production mode at low \tanb.
An example tree-level Feynman diagram for gluon fusion production, which proceeds via
a quark loop, is given in figure \ref{fig:production_mssm}a.
At low \tanb~values this loop is dominated by top quarks, while at 
high \tanb~the b-quark loop dominates. This is a result of the enhanced coupling to down-type fermions at high \tanb. 
Due to the negative top-bottom loop interference effect the gluon fusion cross section decreases with increasing \tanb~up
to around \tanb~$=3$, when the cross section starts to increase with increasing \tanb~again.

@@

There are several different types of \ac{2HDM}, all distinguished by the couplings
of the different Higgs states to bosons and fermions. In its most general
form, there are nine free parameters in the potential of a CP-conserving 2HDM. 
These are taken as \tanb, the mixing angle $\alpha$, already discussed in 
the context of the \ac{MSSM}, the masses of the five Higgs bosons,
and quartic couplings appearing in the potential. The most studied of the
\ac{2HDM}s, the type-II \ac{2HDM}, has a structure very similar to 
the MSSM Higgs sector. The tree-level couplings of the neutral Higgs bosons to 
vector bosons and fermions are the same as the tree-level \ac{MSSM} couplings 
in table \ref{tab:mssm_couplings}. %The decay \AtoZh is also possible,
%the \AtoZh~coupling is proportional to $\cos{(\beta-\alpha)}, like the \Htohh~coupling.

@@

\begin{figure}[h!]
\begin{center}
\subfloat[\PHiggs]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/typeII2HDMxsbr.png}}
\subfloat[\PHiggsps]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/typeII2HDMxsbrA.png}}
\end{center}
\caption[Inclusive production \xsbr for an example of a type-II 2HDM, for the \PHiggs and \PHiggsps boson.]{Inclusive production \xsbr for an example
of a type-II \ac{2HDM}, for (a) the \PHiggs boson and (b) the \PHiggsps boson. The
top figures use \tanb=1 and $\cos{(\beta-\alpha)}=-0.11$, the bottom
figures are made for \tanb=10 and $\cos{(\beta-\alpha)}=-0.02$. At low \tanb~the \Htohh and
\AtoZh decays are enhanced for masses up to $350\,\GeV$ \cite{2HDM-II}.}
\label{fig:2hdm_Hxsbr}
\end{figure}

@@

The parameters that need to be fixed in the benchmark scenarios are the 
\ac{SUSY} breaking scale $M_{\text{SUSY}}$, which is also the mass scale of the third generation squarks.
In addition, the higgsino mass parameter $\mu_{\text{MSSM}}$, and the U(1) and SU(2) gaugino mass parameters, $M_1$ and $M_2$, need to be fixed.
A choice for the masses of the stau ($m_{\tilde{\ell}_3}$) and the gluino ($m_{\tilde{g}}$) also needs to be made. The 
trilinear couplings of the stops, sbottoms and staus to the Higgs field ($A_{\Ptop}$, $A_{\Pbottom}$ and $A_{\Pgt}$) and the 
stop, sbottom and stau mixing parameters ($X_t$, $X_b$ and $X_{\tau}$) are also fixed.

Some of these parameters can be related to each other. For example,
$X_{\Ptop}$, $X_{\Pbottom}$ and $X_{\Pgt}$ can be expressed as:
\begin{equation}\label{eqn:trilinear_couplings}
\begin{split}
&X_{\Ptop} = A_{\Ptop}t-\mu_{\text{MSSM}}\cot{\beta},\\
&X_{\Pbottom} = A_{\Pbottom}-\mu_{\text{MSSM}}\tan{\beta},\\
&X_{\Pgt} = A_{\Pgt} - \mu_{\text{MSSM}}\tan{\beta}.
\end{split}
\end{equation}
In addition, $M_1$ is fixed via the unification
relation,
\begin{equation}
M_1 = \frac{5}{3}M_2\tan{\theta_w}^2.
\end{equation}
%where $\theta_w$ is defined by $\cos{\theta_w} = \frac{m_W}{m_Z}$.
Some additional parameters which only have a
small effect on the MSSM Higgs boson sector are 
fixed to values compatible with 
exclusion limits from direct searches in all benchmark scenarios. The masses
of the first and second generation squarks are set to $1.5\,\TeV$, 
and the masses of the first and second generation sleptons to $500\,\GeV$. The trilinear
couplings of the first and second generation squarks and sleptons are taken to be 0.
%Since the discovery of the 125 GeV Higgs boson, only the MSSM benchmark
%scenarios 
%which contain a light Higgs boson with a mass of around 125 GeV
%are still accessible.
% in the mmax scenario the benchmark values have been chosen h
%such that the mass of the light CP-even Higgs boson is maximized for fixed tanβ and large
%MA (the scale of the soft SUSY-breaking masses in the stop and sbottom sectors, which
%sets the mass scale for the corresponding supersymmetric particles, has been fixed to 1 TeV
%in this scenario). This scenario is useful to obtain conservative bounds on tanβ for fixed
%values of the top-quark mass

\subsection{The $m_{h}^{\text{mod+}}$ scenario}
\label{sec:theory_BSM_models_mhmodp}
The $m_{\PHiggslight}^{\text{mod+}}$ scenario \cite{MSSM-benchmark-scenarios}
is a modification of the $m_{\PHiggslight}^{\text{max}}$ scenario \cite{MSSM-mhmax}. The $m_{\PHiggslight}^{\text{max}}$ scenario, which
was used for interpretations of \ac{MSSM}
 Higgs boson searches at LEP and the Tevatron, allows
the mass of the light Higgs boson to reach the highest a-priori expected 
value of around $135\,\GeV$ for high \mA. There is only a small area of the \mA-\tanb~plane
in this scenario where the mass of the light Higgs boson is compatible with the
observed $125\,\GeV$ state. The modifications to the parameters of the $m_{\PHiggslight}^{\text{max}}$ 
scenario address this issue. In the $m_{\PHiggslight}^{\text{mod+}}$ scenario $M_{\text{SUSY}}$ is chosen
to be $1\,\TeV$. The stop mixing parameter is positive, $X_t= 1.5 M_{\text{SUSY}}$.
%This gives better agreement with muon g-2 results while the mhmod- scenario
%negative stop mixing (-1.9 M_SUSY) results in better agreements with B(b->sgamma) 
%meausrements 
The remaining parameters are set as $\mu_{\text{MSSM}}=200\,\GeV$, $m_{\tilde{g}} = 1.5\,\TeV$,
$m_{\tilde{\ell}_3} = 1\,\TeV$, and $A_{\Pbottom}=A_{\Ptop}=A_{\Pgt}$. 
%Figure \ref{fig:mhmodp_mh}a
%shows the mass of the light Higgs boson in the $m_{h}^{\text{mod+}}$ scenario, showing
%that its mass is compatible with 125 GeV over a large part of the parameter space. Masses within 
%a window $\pm 3$ GeV around 125 GeV are considered compatible with 125 GeV, where the 3 GeV
%variation corresponds to the theoretical uncertainty on the \ac{MSSM} prediction for \mh.

Figure \ref{fig:mhmodp_xs} shows the cross sections of
gluon fusion and b-associated production of the \PHiggs boson 
in the $m_{\PHiggslight}^{\text{mod+}}$ scenario. Gluon fusion 
production dominates at low \tanb, while b-associated production has a larger cross section
at high \tanb. The behaviour of the production cross sections of the \PHiggsps boson
is similar.

@@

Two approches for the definition of an \ac{MSSM} scenario that gives
access to the low \tanb~region have been developed, they will be
discussed in the next sections.

\subsubsection{The low-\tanb~scenario}
\label{sec:theory_BSM_model_lowtb}
In the low-\tanb~scenario \cite{Hein-low-tb-high,MSSM-lowtanb}, the SUSY parameters entering
the radiative corrections are tuned to obtain light 
Higgs boson masses of around $125\,\GeV$ in most of the \mA-\tanb~plane considered.
Figure \ref{fig:mhmodp_mh}b shows that, apart from in a corner of \tanb~1--4 and 
\mA~$150$--$250\,\GeV$, \mh~is compatible with $125\,\GeV$.

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{\PHiggslight}^{\text{mod}+}$ scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_mhmodp.pdf}}
\subfloat[low \tanb~scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_lowtbhigh.pdf}}
\end{center}
\caption[The mass of the light Higgs boson, \mh, as a function of \mA~and
\tanb~in the $m_{\PHiggslight}^{\text{mod+}}$ scenario and the low \tanb~scenario.]{The mass of the light Higgs boson, \mh, as a function 
of \mA~and \tanb~in (a) the $m_{\PHiggslight}^{\text{mod+}}$ scenario and (b) the low \tanb~scenario. The white areas
indicate masses lower than $122\,\GeV$. The figures shows that
the mass of the light Higgs boson is compatible with $125\,\GeV$ over a large
part of the \mA-\tanb~plane in the $m_{\PHiggslight}^{\text{mod+}}$ scenario, except at low \tanb. In the low-\tanb~scenario
the mass of the light Higgs boson is compatible with $125\,\GeV$ nearly everywhere.}
\label{fig:mhmodp_mh}
\end{figure}
%\begin{figure}[h!]
%\begin{center}
%\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_lowtbhigh.png}
%\end{center}
%\caption{Mass of the light Higgs boson in the \mA-\tanb~plane of the low-\tanb~scenario.
%The mass is compatible with $125\,\GeV$ nearly everywhere \cite{MSSM-lowtanb}.}
%\label{fig:lowtbhigh_mh}
%\end{figure}
To obtain \mh$\approx125\,\GeV$ over a large part of the parameter
space, 
$M_{\text{SUSY}}$ is not fixed but varies between a few $\TeV$ and $100\,\TeV$, while
varying the parameter $X_t$ as:
\begin{equation}
\begin{split}
\tan{\beta} \leq 2 &: \frac{X_{\Ptop}}{M_{\text{SUSY}}} = 2,\\
2 < \tan{\beta} \leq 8.6 &: \frac{X_{\Ptop}}{M_{\text{SUSY}}} = 0.0375\text{tan}^2\beta - 0.7\tan{\beta} + 3.25,\\
8.6 < \tan{\beta} &: \frac{X_{\Ptop}}{M_{\text{SUSY}}} = 0.
\end{split}
\end{equation}
The other trilinear couplings are set to $2\,\TeV$, with $\mu_{\text{MSSM}}$ set to $1.5\,\TeV$ and $M_2$ to $2\,\TeV$.

@@

One of the assumptions of the hMSSM is that 
the mass matrix for the neutral CP-even states can
be decomposed as,
\begin{equation}
\label{eqn:hmssm_massmatrix}
\mathcal{M}^2_{\phi} = \mathcal{M}^2_{\text{tree}} + \begin{pmatrix}
\Delta\mathcal{M}^2_{11} & \Delta\mathcal{M}^2_{12} \\
\Delta\mathcal{M}^2_{12} & \Delta\mathcal{M}^2_{22} \end{pmatrix},
\end{equation}
where the $\Delta\mathcal{M}^2_{ij}$ are the radiative corrections.
The second assumption is that only $\Delta\mathcal{M}^2_{22}$ needs to be
taken into account, as this is the element that involves the stop-top correction
and so $\Delta\mathcal{M}^2_{22} \gg \Delta\mathcal{M}^2_{12},\Delta\mathcal{M}^2_{11}$. 
Finally, all SUSY particles are assumed to be heavy enough not to be
detected at the \acs{LHC} and apart from effects on the mass matrix, 
the effects on the Higgs sector can be neglected.
%all SUSY particles are heavy enough to escape detection at the LHC, and their effects on the Higgs sector other than those on the mass matrix, e.g. via direct loop corrections to the Higgs-boson couplings or via modifications of the total decay widths, can be neglected.

Using these assumptions the lightest eigenvalue
of the mass matrix can be inverted to get: 
\begin{equation}
\label{eqn:hmssm_deltam22}
\Delta\mathcal{M}^2_{22} = \frac{m_{\PHiggslight}^2(m_{\PHiggsps}^2+m_{\PZ}^2 - m_{\PHiggslight}^2) - m_{\PHiggsps}^2m_{\PZ}^2\text{cos}^22\beta}{m_{\PZ}^2\text{cos}^2\beta + m_A^2\text{sin}^2\beta - m_{\PHiggslight}^2},
\end{equation}

This means we can write,
\begin{equation}
\label{eqn:hmssm_mHalpha}
\begin{split}
&m^2_{\PHiggs} = \frac{(m_{\PHiggsps}^2+m_{\PZ}^2-m_{\PHiggslight}^2)(m_{\PZ}^2\cos{\beta}^2+m_{\PHiggsps}^2\sin{\beta}^2 - m_{\PHiggsps}^2m_{\PZ}^2\cos{2\beta}^2}{m_{\PZ}^2\cos{\beta}^2+m_{\PHiggsps}^2\sin{\beta}^2-m_{\PHiggslight}^2},\\
&\tan{\alpha} = -\frac{(m_{\PZ}^2+m_{\PHiggsps}^2)\cos{\beta}\sin{\beta}}{m_{\PZ}^2\cos{\beta}^2+m_{\PHiggsps}^2\sin{\beta}^2-m_{\PHiggslight}^2}.
\end{split}
\end{equation}
Combining this with the $\PHiggs$-$\PHiggslight\PHiggslight$ coupling,
\begin{equation}
\label{eqn:hmssm_Hhh}
\lambda_{\PHiggs\PHiggslight\PHiggslight} = \lambda_{\PHiggs\PHiggslight\PHiggslight,\text{tree}} + 3\frac{\Delta\mathcal{M}^2_{22}\sin{\alpha}}{m_{\PZ}^2\sin{\beta}}\cos{\alpha}^2,
\end{equation}
gives enough information to determine the cross sections and branching
ratios of all of the five Higgs bosons as a function of \mA~and \tanb. The scenario
is only well defined in regions where the denominator in equations
\ref{eqn:hmssm_deltam22} and \ref{eqn:hmssm_mHalpha}, $m_{\PZ}^2\cos{\beta}^2+m_{\PHiggsps}^2\sin{\beta}^2 - m_{\PHiggslight}^2$, is nonzero. 
This leads to a minimum accesible \mA~value of \mh~at high \tanb, and
a minimum accessible \mA~of around $151\,\GeV$ for \tanb=1. In addition, the scenario
can be formulated, but is not strictly valid, for values of \tanb~upwards of 10 \cite{CMS-PAS-HIG-16-007}.
The reason for this is that direct higher order SUSY corrections to down-type
fermion couplings and corrections due to SUSY particles in loops become relevant
above \tanb=10, but these are omitted in the hMSSM approach.
